Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-06 ms/LMA_method.Rmd
update method

*Data sources*

We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Table S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
In total, we used `r val$all_sp` woody species and `r val$all_tree` individuals.
The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.

>>>>

*Study sites and plant materials*

We conducted this study in four sites which cover a wide ranges of biomes to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits (see site details in Table S1).
First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
We excluded species that had tiny leaves or leaflets (length <1 cm) because it was not practical to measure leaf disc LMA.
In total, we used `r val$all_sp` woody species and `r val$all_tree` individuals.
The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.

### 2022-05-06 ms/SI.Rmd
update method

# https://github.com/haozhu233/kableExtra/issues/477
options(kableExtra.auto_format = FALSE)
library(kableExtra)

val <- yaml::yaml.load_file("values.yml")
```

@@

@@

```{r, eval=TRUE, echo=FALSE}
tar_load(dm_lm_tab)
dm_lm_tab |>
  kable(format = "html") |>
  kable_styling()
```

>>>>

# https://github.com/haozhu233/kableExtra/issues/47
options(kableExtra.auto_format = FALSE)
library(kableExtra)

val <- yaml::yaml.load_file("../values.yml")
```

@@

| Data name | Site name  | Vegetation                             | Elevation (m) | Locations          | MAT (℃) | MAP (mm) | Dry period (month) | Canopy height (m) | Leaf disc thickness | Leaf punch diameter (cm) | Number of species | Number of individuals |
|-----------|------------|----------------------------------------|---------------|--------------------|---------|----------|--------------------|-------------------|---------------------|--------------------------|-------------------|-----------------------|
| Yunnan    | Bubeng     | Tropical forest (TRF)                  | 780           | 21°37'N, 101°35' E | 21      | 1532     | 6                  | 35-45             | Measured            | 0.6                      | `r val$TRF`       | test                  |
| Yunnan    | Ailao-shan | Subtropical evergreen wet forest (STF) | 2500          | 24°32'N,101°01'E   | 11.7    | 1931     | -                  | 25                | Measured            | 0.6                      | `r val$STF`       | test                  |
| Yunnan    | Yuanjiang  | Hot-dry savanna  (HDS)                 | 480           | 23°28'N, 102°10'E  | 24.7    | 732.8    | 6                  | 4-6               | Measured            | 0.6                      | `r val$HDS`       | test                  |
| Yakushima | Yakushima  | Warm-temperate forest                  | 14 - 1748     | 30°38'N, 130°62'E  | 19.4    | 4477     | -                  | -                 | Not-measured        | 1.0                      | `r val$TRF`       | test                  |

@@

```{r, eval=FALSE, echo=FALSE}
tar_load(dm_lm_tab)
dm_lm_tab |>
  kable(format = "html") |>
  kable_styling()
```
